---
title: "Homework #5"
author: "Lynn Chen"
output: github_document
---

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1: 

```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city,state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```


Let's docus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD") 

baltimore_summary = 
  baltimore_df%>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test =
  prop.test(
    x = baltimore_summary %>% pull(unsolved), 
    n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy() ## takes output of the prop.test and organize as a dataframe
```


Let's try to iterate across cities ! 

1) Write a function and test on several cities.

```{r}
prop_test_function = function(city_df){

  city_summary = 
    city_df%>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test =
    prop.test(
      x = city_summary %>% pull(unsolved), 
      n = city_summary %>% pull(n))
  
  return(city_test)

}

prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()

```

Iterate across all cities,

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Make a plot showing estimates and confidence interval. 

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results= map(test_results, broom::tidy)
  ) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2:

Create a tidy dataframe containing data from all participants.

```{r}
study_df = 
  tibble(files = list.files("./data/", full.names = TRUE)) %>% 
  mutate(data = purrr::map(.x = files, read_csv)) %>% 
  separate(files, into = c("group", "subject_id"), sep = "_", remove = T) %>% 
  mutate(group = case_when(str_detect(group, "exp") ~ "Experiment",
                               str_detect(group, "con") ~ "Control"),
         subject_id = str_replace(subject_id, ".csv", "")) %>%
  unnest(data) %>% 
  pivot_longer(cols = week_1:week_8, names_to = "week", values_to = "observation") %>%
  mutate(week = as.numeric(parse_number(week)))
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
study_df %>% 
  ggplot(aes(x = week, y = observation, color = subject_id)) + 
  geom_line() +
  facet_grid(~group) + 
  labs(
    title = "Observations Over Time by Study Arm",
    subtitle = "for an eight week observation period",
    x = "Week",
    y = "Observation",
    color = "Subject ID")
```

From the plot, we can observe that over the 8 week observation period, participants in the experimental group gradually shows higher observation values in comparison to the control group, especially during the first 3 weeks. In addition, observations in control group oscillates consistently over the same values through out the 8 weeks duration and show no significant difference, while the experiment group shows a positive trend overtime. 


## Problem 3: 


```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

Write a function that takes a vector as an argument; replaces missing values using the rules.

```{r}
Replace_missing_values = function(x){
  
  if(is.numeric(x)){
    x = replace_na(x, mean(x, na.rm = TRUE))
    }
  else if(!is.numeric(x)){
    x = replace_na(x, "virginica")
    }
  return(x)
}

iris_with_missing = 
  tibble(map_df(iris_with_missing, Replace_missing_values))

iris_with_missing

```

